HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

We now describe the HUME annotation interface, shown in Figure~\figref{fig:interface}. 
%We turn to discuss the interface for collecting human judgements on the semantic units
%of the source, relating to the translation. 
UCCA annotations of the source are done offline,
using the UCCA web application.
%\figref{fig:interface} presents the user interface of HUME. 
The translation appears at the top, and
the source sentence directly below it. Underneath the source sentence appears
its list of semantic units. 
%For each semantic unit, including the one for the
%entire source sentence, there is a textbox, displaying the yield of that unit.
%Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
The user is asked to select a label for each unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the right of the unit's box.
Note that the UCCA labels are not shown.

The interface presents, for each unit, the translation segment aligned with it.
This allows the user, especially in long sentences, to focus her attention on the parts
most likely to be relevant for her judgement. As the alignments are automatically derived,
and therefore noisy, the annotator is instructed to treat the aligned text is a cue, but to ignore
the alignment if it is misleading, and instead 
make a judgement according to the full translation sentence.

>>>>

We now describe the HUME annotation interface, shown in \figref{fig:interface}. 
%We turn to discuss the interface for collecting human judgements on the semantic units
%of the source, relating to the translation. 
UCCA annotations of the source are done offline,
using the UCCA web application.
%\figref{fig:interface} presents the user interface of HUME. 
The translation appears at the top, and
the source sentence directly below it. Underneath the source sentence appears
its list of semantic units. 
%For each semantic unit, including the one for the
%entire source sentence, there is a textbox, displaying the yield of that unit.
%Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
The user is asked to select a label for each unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the right of the unit's box.
Note that the UCCA labels are not shown.

The interface presents, for each unit, the translation segment aligned with it.
This allows the user, especially in long sentences, to focus her attention on the parts
most likely to be relevant for her judgement. As the alignments are automatically derived,
and therefore noisy, the annotator is instructed to treat the aligned text is a cue, but to ignore
the alignment if it is misleading, and instead 
make a judgement according to the full translation.
